---
title: "Institutionalization"
format:
  html:
    toc: true
    css: prep/styles.css
execute: 
  warning: false
  message: false
  error: false
  echo: false
editor: visual
---

```{r}
source(here::here("./prep/prep.r"))
source(here::here("./scripts/00 cleaning script.R"))
source(here::here("./scripts/01 descriptives.R"))
source(here::here("./scripts/01 analysis script.R"))
source(here::here("./scripts/01 analysis subgraphs script.R"))
source(here::here("./scripts/01_geographic_network.R"))

```

::: definition_box
**Institutionalization** is defined as the extent to which ecosystem actors' work will endure beyond 2024.
:::

Numerous organizations are working to ensure that Nigeria's governmental and non-governmental actors possess the talent and systems to implement accountability work into the future.

[**Finding 16. “On Nigeria grantees have deployed capacity building approaches and digital tools to successfully build the skills and human capital of other ecosystem actors, including journalists, public officials, ACAs, and their partners’ staff.**]{style="color: #00457c;"}

::: box
Let me start by saying the focus of our own work is on institutionalizing behavior change approaches to reduce corruption in the public and private sectors in Nigeria. And basically we are working with the various programs that we are implementing at NIPSS which has to do with the training of high level policy actors in Nigeria. So that's the focus of our work. *--Behavior Change FGD participant*
:::

One grantee each from JoinBodi, Media and Journalism, Behavior Change, and Criminal Justice are building capacity of staff in MDAs or ACAs. This includes grantees like Policy and Legal Advocacy Centre (PLAC) who are building capacity of gender and inclusion desk officers at INEC to ensure inclusive election processes, Centre for Journalism Innovation and Development (CJID) building fact-checking capabilities at the National Orientation Agency (NOA), and Legal Defence and Assistance Project (LEDAP) building e-learning platforms for the Economic and Financial Crimes Commission (EFCC) and the National Bar Association (NBA) as well as building ICPC capacity in asset tracing. National Institute for Policy and Strategic Studies(NIPSS) also trains policy actors in accountability and integrity.

Three of the four of the Criminal Justice FGD participants were able to institutionalize some of their initiatives within MDAs, (one is working on an initiative that has potential for institutionalization) along with one Behavior Change grantee. The Criminal Justice grantees have had the most success with developing technological tools the agencies have supported and adopted, while the Behavior Change grantee has been able to institutionalize SME governance standards. Figure 17 provides several examples that were highlighted during FGDs.

```{r, fig.cap="Figure 17. Examples of On Nigeria grantees successfully institutionalizing systems and tools with their partners."}

innov_table <- readxl::read_xlsx(here::here("./data/institutional_table.xlsx"))

flex_fun(innov_table)


```

::: box
"And let me talk about the collaboration with the UN Global Compact Local Network in Nigeria and the Lagos Chamber of Commerce in setting the standard for conduct of governance within SMEs in Nigeria. So let me start with the end. The end result is that we now have a Financial Reporting Council issued corporate governance guidelines for SMEs in Nigeria. So now we have a standard for all SME governance in Nigeria." *-Behavior Change grantee*

"We also discovered that all the ACAs, the Anti Corruption agencies needs to have a platform where information can be assessed, where information can be gotten. And we also came up with what we call the web portal for the ACAs. This web portal is a community of practice on information sharing among themselves and it is currently domiciled with the EFCC." *–Criminal Justice grantee*

"So we worked with especially the state anti corruption units in kano, in Oyo state, in Kaduna and in Jigawa to put up what they call the Sharata. The Sharata is a platform, a reporting app where citizens can actually report cases of criminalities and issues that all these anti corruption agencies can go after. And it is it, it tends to keep away the fact that the citizen, if the cases have been reported, they won't find, they won't trace the person who is reporting the cases. So it is an open platform for such kind of report cases." *–Criminal Justice grantee*
:::

[**Finding 17. everal grantees highlighted that their initiatives are financially sustainable, and will endure beyond the closure of On Nigeria grant funding.**]{style="color: #00457c;"}

Palace of Priests noted that their various platforms (Ministers Against Corruption, the Christian Women Against Corruption and the Youth Vanguard Against Corruption) no longer require funding. They allow for ongoing anticorruption dialogue despite grant funding ending. Additionally, LEDAP was able to work with EFCC to incorporate their e-learning platform costs into their budget to ensure that as their grant funding ends the platform can endures for EFCC’s training needs.

::: box
"In terms of what worked well in terms of our collaboration, the platforms that we are able to establish, especially the three national platforms, which is the Ministers Against Corruption, the Christian Women Against Corruption and the Youth Vanguard Against Corruption that were established at both state and national levels, was able to strengthen our grassroots engagement. And these platforms are actually key to our sustainability plan because as we speak, even with the absence of funding, there are still anticorruption discussions that are still going on in these platforms." *--Behavior Change FGD participant*
:::
