---
title: "On Nigeria 2.0"
subtitle: "Endline Social Network Analysis Report"
author: "Brian Calhoon and Randi Rumbold"
format:
  html:
    toc: true
    embed-resources: true
    css: prep/styles.css
execute: 
  warning: false
  message: false
  error: false
  echo: false
editor: visual
---

```{r}
source(here::here("./prep/prep.r"))
source(here::here("./scripts/00 cleaning script.R"))
source(here::here("./scripts/01 descriptives.R"))
source(here::here("./scripts/01 analysis subgraphs script.R"))
source(here::here("./scripts/01 analysis script.R"))
source(here::here("./scripts/01_geographic_network.R"))

```

# Executive Summary

# Introduction

The MacArthur Foundation’s Big Bet On Nigeria program supports Nigerian-led efforts to reduce corruption by strengthening accountability, transparency, and participation. A resilient accountability ecosystem—the networks of relationships “between citizens and governing authorities … \[and\] other important actors, including media, private sector, diverse organized citizen groups, and various actors within the state itself” that collectively support social accountability—is essential to the success and sustainability of On Nigeria’s anticorruption programming (for more on accountability ecosystems, see [Halloran’s Accountability Ecosystems: The Evolution of a Keyword)](https://accountabilityresearch.org/accountability-ecosystems-the-evolution-of-a-keyword/).

This social network analysis (SNA) report explores how On Nigeria grantees collaborate with other actors in the broader accountability ecosystem and with each other, the outcomes to which collaboration contributes, and how and to what end collaborative networks might be further strengthened, **to bolster anticorruption efforts**. To do this, the report will investigate the ecosystem elements of collaboration, diversity, adaptive resilience, institutionalization, and scale.[^sna_report_endline-1] As a result, this report directly addresses the evolution of the accountability ecosystem (the "trunk" of On Nigeria's theory of change").

[^sna_report_endline-1]: These elements are contained in the Portfolio Rubrics of the Final Evaluation design.

# Methodology

## Overview

In October 2024, the evaluation team (ET) held a workshop in Abuja, Nigeria with On Nigeria grantees in all four cohorts (Behavior Change, Criminal Justice, Joinbodi, and Media and Journalism). Each grantee identified their primary partners, and in November 2024, the ET followed up with each grantee via survey to identify additional partner relationships. In January 2025, the ET sent a survey to non-grantee organizations that were identified by grantees as connections to develop a more robust network.

To clean, analyze, and visualize the endline network data, the ET used the R programming language. To provide additional context around the network statistics, the ET used the network's existing structure to generate a sample of 1,000 similar networks and calculated average network statistics for those networks. This provides a point of comparison for the actual network's network statistics. In addition, the ET mapped the organizations to their respective states on an interactive map of Nigeria to better visualize the geographic make up of the organizations and their connections. A list of R packages used for the analysis is included in Annex X. This online report was rendered using Quarto.

The survey was supplemented with six focus group discussions (FGDs) with grantees (4 FGDs) and non-grantees (2 FGDs) in February 2025. Respondents all represented voice actors and were primarily from NGOs. There was one INGO represented in the Criminal Justice FGD, six participants represented private businesses (primarily media organizations), and one government entity was represented in the Joinbodi session. In terms of geography, fourteen participants organizations are based in the Federal Capital Territory (FCT), nine were based in Lagos, two were from Kano, and one each were from Kaduna, Kwara, Plateau, and Akwa Ibom. Six respondents were female, while the rest were male. Finally the cohort breakdown was: four Criminal Justice grantees, eight Joinbodi grantees, seven Media and Journalism grantees, four Behavior Change grantees, and six non-grantees. The FGDs were all conducted remotely over Zoom, and the transcripts were analyzed using CoLoop.

## Understanding Social Networks

Networks are used to understand interactions. These interactions can be across people, organizations, roads, or items people purchase on the internet. In this case, we are trying to understand the interactions between organizations. In network-speak, the organizations in the network are "nodes" and the connections between nodes are "edges".

### The Baseline Data

For the baseline SNA, the ET distributed an online survey to On Nigeria grantees in all four cohorts (Behavior Change (BC), Criminal Justice (CJ), Joinbodi (JB), and Media and Journalism (MJ)) and their non-grantee (NG) partners, and conducted FGDs with a subset of grantees. Baseline data was collected in 2022 **Is this precise enough? Can we say what month(s)?**. The baseline SNA dataset included 127 organizations and captured 197 unique interactions.

### The Endline Data

The Endline network of On Nigeria grantees and partners consists of `{r} gorder(g_non)` organizations and `{r} gsize(g_non)` connections. The relationships between and among these organizations are the focus of this network analysis. The nodes consist of `{r} length(dat5_non5$grantee[dat5_non5$grantee=="Grantee"])` grantees and `{r} length(dat5_non5$grantee[dat5_non5$grantee=="Non Grantee"])` non-grantees.

The network is made up of different types of organizations. The most common type of organization is a non-governmental organiztion (NGO) which makes up `{r} ngo_orgs` percent[^sna_report_endline-2] of all the organizations. This represents a `{r} 63 - ngo_orgs` percent decrease in the percent of NGOs in the endline network compared to the baseline network. The next most frequent organization type are government agencies, making up `{r} govt_orgs` percent[^sna_report_endline-3] which is consistent with the baseline network (24 percent). There are `{r} private_orgs` percent[^sna_report_endline-4] private businesses, an increase of `{r} private_orgs - 13` percent from the baseline. Finally, international NGOs (INGOs) make up `{r} ingo_orgs` percent[^sna_report_endline-5] of the endline network.

[^sna_report_endline-2]: `{r} length(dat5_non5$desc_org[dat5_non5$desc_org=="NGO"])` organizations

[^sna_report_endline-3]: `{r} length(dat5_non5$desc_org[dat5_non5$desc_org=="Government Agency"])` organizations

[^sna_report_endline-4]: `{r} length(dat5_non5$desc_org[dat5_non5$desc_org=="Private Business/Company"])` organizations

[^sna_report_endline-5]: `{r} length(dat5_non5$desc_org[dat5_non5$desc_org=="INGO"])` organizations

Of the `{r} gsize(g_non)` connections in the endline network, `{r} round(reciprocity(g_non)*100, 0)` percent are confirmed, and `{r} round(100-reciprocity(g_non)*100, 0)` are unconfirmed.[^sna_report_endline-6] This represents an increase in confirmed connections of `{r} round(reciprocity(g_non)*100, 0) - 13` percent. To be certain, this statistic is affected by non-responses. If only one organization in a pair responded to the survey, then the interaction cannot be confirmed. For the endline survey, there was an extra effort made to follow up with grantees and to contact non-grantees, and this is reflected in the increase in confirmed connections.

[^sna_report_endline-6]: A confirmed connection means that both organizations in a pair identified the connection, and an unconfirmed connection means that only one organization in a pair identified the connection.

## Limitations

There are limitations to the data. There is a snapshot of data from the baseline (2021) and a snapshot of data from the endline (2024-2025). Since participation was voluntary, there may be gaps in representation, particularly among smaller organizations. The response rates for the endline survey were 69 percent for grantees and 53 percent for non-grantees.[^sna_report_endline-7]

[^sna_report_endline-7]: There were an additional 16 grantee organizations who started the survey but did not provide information on their partnerships.

It is likely that survey fatigue affected responses as well. In addition, each time a new partner was added, it meant that a respondent had to go through the same series of questions again. This likely means that the included partnerships are not exhaustive due to time or an individual respondent's knowledge. On Nigeria subgrantees were not specifically included in the survey sample, although some sub-granting grantees mentioned them as partners. However, the data do not distinguish between non-grantee organizations and On Nigeria subgrantees. Therefore, the data might also understate the depth of connection some organizations represented as non-grantees have to the overall network. Neither the online survey nor FGDs contained any questions specifically focused on collaboration related to gender equity and social inclusion (GESI) activities or considerations. Data for analysis of this component were based on mentions of GESI made during the FGDs and open-ended survey questions. Thus, the data on this may not provide a complete picture. Finally, it is important to emphasize that there is no inherent judgment associated with the specific value of any network statistic—they are all context specific: a very high density or centrality score, for example, is not necessarily desirable, as it may not be efficient or effective for every network actor to be connected to all, or even many, others. Rather, collaborations covered in this report should be understood within the context of each network actor’s goals and activities. In an attempt to help the reader understand the network statistics, the ET generated 1,000 similar networks based on the actual network structure and calculated average centrality statistics as a benchmark against which to compare the actual network statistic averages.

# Findings

The primary research question that this SNA contributes to is, \*\*to what extent, and in what ways (expected and unexpected), did On Nigeria 2.0 contribute to broadening,

::: box-right
\_**On Niger Anticorruption Ecosystem Elements**

-   Collaboration
-   Diversity
-   Adaptive resilience
-   Institutionalization
-   Scale
:::

deepening, and strengthening a diverse, robust, and self-sustaining accountability ecosystem in Nigeria?\*\*

The report explores the maturity of ecosystem elements to help understand how the On Nigeria Accountability Network is evolving in its collaboration, diversity, adaptive resilience, institutionalization, and scale.

## Collaboration

This analysis explores the levels of engagement of On Nigeria grantees with other grantees and with non-grantees as well as across types of organizations and cohorts. Where there are connections, organizations typically operate at high levels of collaboration and frequently. Figure 1 presents the overall network map for all On Nigeria grantees and their non-grantee partners.

::: panel-tabset
## The Whole Network

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%", fig.cap="Figure 1. The entire network displayed with cohorts by color and grantee by shape."}


#| fig-align: "center"
#| fig-width: 12
#| out-width: 100%

subtitle <- "<span style = 'font-size:18pt; color:#0964B0;'>**Behavior Change Cohort**</span>, <span style = 'font-size:18pt; color:#B5984F;'>**Media and Journalism Cohort**</span>, <span style = 'font-size:18pt; color:#E17F48;'>**Criminal Justice Cohort**</span>, <br><span style = 'font-size:18pt; color:#5B507A;'>**JoinBodi Cohort**</span>" 


#Main graph
ggraph(g_non, layout = "stress") +
  geom_edge_bundle_force(edge_color = "lightgrey", edge_linewidth = .8, alpha = .8
                  , arrow = arrow(angle = 15, length = unit(.05, "inches")
                                  , ends = "last", type = "closed")) +
  geom_node_point(aes(size = degree, shape = grantee), color = "white") +
  geom_node_point(aes(size = degree, shape = grantee, color = cohort)) +
  #geom_node_text(aes(filter = degree >= 9, label = names_pretty), size = 4, repel = TRUE) +
  scale_size(range = c(2, 12)) +
  scale_color_manual(values = palette)+
  labs(title = "The Endline On Nigeria Accountability Network"
       , subtitle = subtitle
       , shape = ""
       , size = "Degree")+
  theme_graph() +
  theme(legend.position = "bottom"
        , legend.text = element_text(size = 14)
        , legend.title = element_text(size = 16)
        , plot.subtitle = element_markdown()
        , plot.title = element_text(size = 20)) +
  guides(color = "none", fill = "none"
         , shape = guide_legend(override.aes = list(size = 6)))

```

## The Whole Network: Type of organization

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%", fig.cap="Figure 1. The entire network displayed with cohorts by color and type of organization by shape."}


#| fig-align: "center"
#| fig-width: 12
#| out-width: 100%

subtitle <- "<span style = 'font-size:18pt; color:#0964B0;'>**Behavior Change Cohort**</span>, <span style = 'font-size:18pt; color:#B5984F;'>**Media and Journalism Cohort**</span>, <span style = 'font-size:18pt; color:#E17F48;'>**Criminal Justice Cohort**</span>, <br><span style = 'font-size:18pt; color:#5B507A;'>**JoinBodi Cohort**</span>" 


#Main graph
ggraph(g_non, layout = "stress") +
  geom_edge_bundle_force(edge_color = "lightgrey", edge_linewidth = .4, alpha = .8
                  , arrow = arrow(angle = 15, length = unit(.05, "inches")
                                  , ends = "last", type = "closed")) +
  geom_node_point(aes(size = degree, shape = desc_org), color = "white") +
  geom_node_point(aes(size = degree, shape = desc_org, color = cohort)) +
  #geom_node_text(aes(filter = degree >= 9, label = names_pretty), size = 4, repel = TRUE) +
  scale_size(range = c(2, 12)) +
  scale_color_manual(values = palette)+
  scale_shape_manual(values = c("Private Business/Company" = 17, "NGO" = 16, "Government Agency" = 15, "INGO" = 18))+
  labs(title = "The Endline On Nigeria Accountability Network"
       , subtitle = subtitle
       , shape = "Type of Org."
       , size = "Degree")+
  theme_graph() +
  theme(legend.position = "bottom"
        , legend.text = element_text(size = 12)
        , legend.title = element_text(size = 14)
        , plot.subtitle = element_markdown()
        , plot.title = element_text(size = 20)) +
  guides(color = "none", fill = "none", shape = guide_legend(nrow=2, override.aes = list(size = 5))
  )

```
:::

Among all connections, respondents rated `{r} df_collab$percent_high` percent[^sna_report_endline-8] of them as highly collaborative. This means that there is frequent communication, long-term interaction and coordination, and that the partners share ideas and resources. In particular, high collaboration was reported among non-grantee--grantee relationships where `{r} df_collab_grantee |> filter(from_grantee == "Non Grantee", to_grantee == "Grantee") |>  pull(percent_high)` percent.[^sna_report_endline-9] were considered high collaboration. Figure 2 shows levels of collaboration among grantees and non-grantees. Notably, only four percent of all collaborations were considered low. Low level collaboration refers to infrequent networking and/or infrequent information sharing.

[^sna_report_endline-8]: `{r} df_collab$n_high` connections

[^sna_report_endline-9]: `{r} df_collab_grantee |> filter(from_grantee == "Non Grantee", to_grantee == "Grantee") |>  pull(n_high)` connections

```{r, fig.cap="Figure X: The majority of collaborations were rated as high, and this was especially true among non-grantee to grantee connetions."}

df_collab_grantee_ft

```

In FGD discussions the beneficial role of the cohort was highlighted by grantees and non-grantees alike with participants referencing the supportive collaboration and inherent trust of other members. The cohorts serve as a space for like-minded organizations to interact more often than they otherwise would. Participants noted how this frequent collaboration was required to foster effective collaborative partnerships.

::: box-left
"We have good working relationship with some of our cohort members as well as now we have what we call like an annual conference for the MAJ Cohort, for example, which all the partner organizations under the cohort are going to participate in. So every year would host a conference and this. I don't know if that would happen this year but we've been able to do it for over three, the last three years. And I believe that would also be able to come together to still run some things like that." *--Media and Journalism cohort, FGD participant*
:::

Survey data supports this view that the cohorts are useful collaboration mechanisms with nearly all respondents reporting that the level of cohort--cohort collaboration is either high or medium.

```{r, fig.cap="Figure X: Intra cohort collaborations were almost always rated as either high or medium, meaning that these partners are engaging in longer term sharing and partnerships."}

df_collab_cohort |> 
  dplyr::select(From, To, 'High Collaboration', 'Medium Collaboration', 'Low Collaboration') |> 
  filter(From == To) |> 
  flex_fun()

```

[**Finding 1: The overall network density is lower than any individual cohort's density.**]{style="color: #00457c;"}

The density of the overall network is `{r} round(density_non_end*100, digits = 0)` percent. This aligns with the density of the baseline study, and should be read as neither high nor low. The densities of individual cohort neighborhoods are higher than the overall network. A cohort neighborhood includes those organizations that are in the cohort, and organizations that cohort members are directly connected to. The quote below illustrates how cohorts are useful even for those outside of the formal cohort.

::: box
"In collaborating with other organizations, particularly with CISLAC we have this quarterly opportunity to meet all the organizations that were under the CISLAC cohorts. So we compare notes and we share experiences and then learn from each other. That was very, very effective... When you are doing something and sometimes you may lack a little knowledge on how best to go about it, you can call on a partner who might also have that relationship the other way around. And then it works out." *--Non Grantee FGD participant*
:::

This ensures that the full effect of cohorts as organizing bodies is captured in the findings. The criminal justice neighborhood has the highest density but is also the smallest neighborhood with only 31 organizations.\[\^sna_report_endline-10\]

There are a few organizations that operate as central hubs in the network, both within and across modules. With the exception of Media and Journalism grantees, grantees tend to collaborate most with non-grantees or with grantees in their own module. Yet, within and across modules, the ratio of realized connections to all possible connections remains quite low.

```{r, fig.align="center", fig.width=6, fig.height=4, out.width="80%"}

density_df <- data.frame(network = c("Behavior Change", "Criminal Justice", "JoinBodi", "Media and Journalism", "Overall")
                                     , density = c(bechange_nbhd_density, crimjust_nbhd_density, joinbodi_nbhd_density, medjourn_nbhd_density, g_non_density)) |> 
                                mutate(density = round(density*100, digits = 0))


ggplot(density_df)+
  geom_col(aes(x = density, y = fct_reorder(network, density))
           , fill = "#00457C", width = .6) +
  geom_text(aes(x = density, y = fct_reorder(network, density)
                , label = paste0(density, "%"))
            , hjust = 1.25, color = "white"
            , fontface = "bold")+
  theme_void() +
  theme(axis.text.y = element_text(color = "black", size = 10, hjust = 1)
        , axis.title.x = element_text(size = 10, face = "bold")
        , plot.title = element_text(size = 12, face = "bold")
        , plot.title.position = "plot"
        , plot.margin = unit(c(10,10,20,10), "pt")) +
  labs(x = "Density"
       , title = "Figure X. Network density for the overall network \nand individual cohort-level neighborhoods.") 
  

```

[**Finding 2: Key organizations in connecting the overall network are primarily from the Media and Journalism and JoinBodi cohorts.**]{style="color: #00457c;"}

To better understand the key organizations in the overall network, Figure 3 presents a centrality layout. The organizations closer to the middle, with larger bubbles, and with labels play are more important role in connecting the different parts of the overall network. The five most prominent organizations filling this role in the overall network are Wole Soyinka Centre for Investigative Journalism (WSCIJ), Progressive Impact Organization for Community Development (PIOCD), Daily Trust Foundation (DTF), and the Centre for Information Technology and Development (CITAD). It is also worth noting that the cohorts of Media and Journalism and JoinBodi are well represented in Figure 3, with Behavior Change also appearing. The Independent Corrupt Practices Commission (ICPC), formerly a grantee, and WikkiTimes Media, Ltd. (WKTL) also play this important role from outside the formal grantee network.

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%", fig.cap="Figure 3. Hub organizations are located closer to the center. These hubs act as connectors across the whole network."}

#| fig-align: "center"
#| fig-width: 12
#| out-width: 100%

subtitle <- "<span style = 'font-size:18pt; color:#0964B0;'>**Behavior Change Cohort**</span>, <span style = 'font-size:18pt; color:#B5984F;'>**Media and Journalism Cohort**</span>, <span style = 'font-size:18pt; color:#E17F48;'>**Criminal Justice Cohort**</span>, <br><span style = 'font-size:18pt; color:#5B507A;'>**JoinBodi Cohort**</span>" 
ggraph(g_non, layout = "centrality", cent = igraph::betweenness(g_non))+
  geom_edge_bundle_force(edge_color = "lightgrey", edge_linewidth = .4, alpha = .8
                       , arrow = arrow(angle = 15, length = unit(.05, "inches")
                                       , ends = "last", type = "closed"), threshold = .4, n_cycle = 2) +
  geom_node_point(aes(size = igraph::betweenness(g_non), shape = grantee), color = "white") +
  geom_node_point(aes(size = igraph::betweenness(g_non), shape = grantee, color = cohort)) +
  geom_node_text(aes(filter = igraph::betweenness(g_non) >= quantile(igraph::betweenness(g_non), .9), label = acronym), size = 6, repel = TRUE) +
  scale_size(range = c(1, 12)) +
  scale_color_manual(values = palette)+
  labs(title = "Key Connectors in the On Nigeria Accountability Network"
       , subtitle = subtitle
       , shape = "Grantee"
       , size = "Degree")+
  coord_fixed() +
  theme_graph() +
  theme(legend.position = "bottom"
        , legend.text = element_text(size = 14)
        , legend.title = element_text(size = 16)
        , plot.subtitle = element_markdown()
        , plot.title = element_text(size = 20)) +
  guides(color = "none", fill = "none")

```

## Diversity

**Finding 3: The On Nigeria Anticorruption Network includes multiple types of organizations that collaborate with each other and seek out new and diverse partnerships.**

The most common type of organization is a non-governmental organiztion (NGO) which makes up `{r} ngo_orgs` percent[^sna_report_endline-10] of all the organizations. This represents a `{r} 63 - ngo_orgs` percent decrease in the percent of NGOs in the endline network compared to the baseline network. The next most frequent organization type are government agencies, making up `{r} govt_orgs` percent[^sna_report_endline-11] which is consistent with the baseline network (24 percent). There are `{r} private_orgs` percent[^sna_report_endline-12] private businesses, an increase of `{r} private_orgs - 13` percent from the baseline. Finally, international NGOs (INGOs) make up `{r} ingo_orgs` percent[^sna_report_endline-13] of the endline network. These organizations exist across the cohorts and collaborate regularly with each other.

[^sna_report_endline-10]: `{r} length(dat5_non5$desc_org[dat5_non5$desc_org=="NGO"])` organizations

[^sna_report_endline-11]: `{r} length(dat5_non5$desc_org[dat5_non5$desc_org=="Government Agency"])` organizations

[^sna_report_endline-12]: `{r} length(dat5_non5$desc_org[dat5_non5$desc_org=="Private Business/Company"])` organizations

[^sna_report_endline-13]: `{r} length(dat5_non5$desc_org[dat5_non5$desc_org=="INGO"])` organizations

```{r}

df_collab_desc_org |> 
  mutate(percent_high = paste0(percent_high, "%", " (", n_high, ")")
         , percent_med = paste0(percent_med, "%", " (", n_med, ")")
         , percent_low = paste0(percent_low, "%", " (", n_low, ")")
         , Total = paste0(round(total/sum(total)*100, digits = 0), "%", " (", total, ")")) |> 
  select("From" = from_desc_org
         , "To" = to_desc_org
         , "High Collaboration" = percent_high
         , "Medium Collaboration" = percent_med
         , "Low Collaboration" = percent_low
         , Total) |> 
  flex_fun()

```

[**Finding 4: Cohort neighborhoods have diverse structures of hubs and organizations.**]{style="color: #00457c;"}

The Cohort neighborhoods are subnetworks of the overall network. They are defined as including those organizations that are part of each cohort and those organizations who are direct connections of cohort members. In this construction, the neighborhoods' hub organizations may include organizations that are not part of the cohort. Figures 4-7 display centered hub organizations and the neighborhoods' connections. [Annex 1 contains maps of each cohort network within the overall netwok.](#%20Annex%201)

The JoinBodi neighborhood has multiple hubs from its cohort as well as the Media and Journalism and the Behavior Change cohorts.

::: panel-tabset
## JoinBodi

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%", fig.cap="Figure 4. The JoinBodi neighborhood has many actors serving as hub organizations and connecting its different parts."}

graph_nbhd_centrality_fun(graph = joinbodi_nbhd
                          , title = "Key connecting organizations in the JoinBodi Neighborhood")

```

## Behavior Change

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%", fig.cap="Figure 5. The Behavior Change neighborhood a few key organizations serving as hub organizations. This visualization removes organizations that were not connected to the main cluster in this neighborhood."}

graph_nbhd_centrality_fun(graph = bechange_nbhd_main
                          , title = "Key connecting organizations in the Behavior Change Neighborhood")

```

## Media and Journalism

```{r, , fig.align="center", fig.width=12, fig.height=10, out.width="100%", fig.cap="Figure 6. The Median and Journalism neighborhood has one key organization acting as its hub, and it is supported by lesser hub organizations."}

graph_nbhd_centrality_fun(graph = medjourn_nbhd
                          , title = "Key connecting organizations in the Media and Journalism Neighborhood")

```

## Criminal Justice

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%", fig.cap="Figure 7. The Criminal Justice neighborhood has three hub organizations that connect its network.  This visualization removes organizations that were not connected to the main cluster in this neighborhood."}

graph_nbhd_centrality_fun(graph = crimjust_nbhd_main
                          , title = "Key connecting organizations in the Criminal Justice Neighborhood")

```
:::

**Finding 5: Grantees are working to increase the number of individuals involved in the accountability ecosystem through outreach and capacity building, especially for women and youth.**

FGD participants highlighted how they proactively and intentionally seek out new individuals to participate in their programs or new organizational partnerships. In the Behavior Change cohort, the Palace of Priests Assembly created three national platforms to promote discussions on anticorruption. Two of these coalitions are the Christian Women Against Corruption and Youth Vanguard Against Corruption. Also in the Behavior Change cohort, Al-Habibiyyah Islamic Society works with Mambayyah House and Small and Medium Enterprises Development Agency of Nigeria (SMEDAN) to provide anticorruption outreach to youth as well as entrepreneurial and digital skills training.

::: box
"We were able to learn a lot from issues that affect women, especially with disability. We were also able to upscale their skill in the area of issues that has to do with disability law policy frameworks and how to push an agenda for a sustainable environment, a sustainable society that actually embraces all." *--Media and Journalism FGD participant*
:::

Through this combination, Al-Habibiyyah believes that financial security can allow people to become accountability advocates in their community. Women Radio outlined a collaboration with Premium Times and Wole Soyinka Centre for Investigative Jouralism (WSCIJ) to train female journalists at the women radio center in all states. Included in their series “Pivotal” was sexual and gender-based violence and gender equity issues. Their collaboration allowed for wider dissemination and amplification of the show.

To encourage youth engagement Daria Media focused a presidential townhall series around universities and WSCIJ works with communications students in order to ensure the next generation of journalists is ready to work. From the JoinBodi cohort, youth focused initiatives include supporting anticorruption clubs at secondary schools in Kano, and a similar initiative in Borno. BudgIT encourages and teaches youth how to actively engage with government representatives.

In addition, participants from all FGDs talked about seeking out partnerships with organizations that align with their goals. A few participants also discussed selecting partners based on expertise and strengths. This can be for two reasons: 1) so that partners work on different but complementary activities or roles (such as amplifying a message or story by another organization, acting as the convener for a group of diverse organizations who conduct technical work, etc.), and 2) for mentorship, capacity building, or general knowledge sharing. Finally, outreach can be to groups in different geographies which can help an organization to reach local or grassroots populations or students/congregants, or working with those with access to particular ministries, departments, and agencies (MDAs).

All of these outreach efforts contribute to the diversity of the On Nigeria network and their interactions with their subgrantees and non grantee partners.

**Finding 6: The On Nigeria anticorruption network works in all states.**

The map below shows the geographic reach of the On Nigeria anticorruption network. The organizational headquarters are shown in approximate locations based on their state, and the individual states are shaded based on how many organizations work in the state. Each cohort is also represented in each state.

```{r, fig.width=10, fig.align="center", out.width="100%"}

tm

```

# Conclusions

-   The cohorts function well and serve as a useful space for longer-term relationships and collaboration across partners.

-   On Nigeria grantees seek out new partnerships and opportunities to learn from each other.

-   Will read this in the coming days and flesh out the conclusions.

# Annexes

## Annex 1: Additional Tables, Charts, and SNA Maps

### An interactive map of the On Nigeria anticorruption network.

```{r}

#| out-width: 100%
#| fig-cap: "Click on a node to see the organization name and centrality statistics"

V(g_non)$group <- V(g_non)$cohort
V(g_non)$title <- paste0("<b>Org:</b> ", V(g_non)$name, "<br><b>Cohort:</b> ", V(g_non)$cohort
                     , "<br><b>Degree:</b> ", V(g_non)$degree, "<br><b>Between:</b> ", V(g_non)$betweenness                     , "<br><b>Centrality:</b> ", V(g_non)$centrality, "<br><b>Eigen:</b> ", V(g_non)$eigen)
V(g_non)$degree <- igraph::degree(g_non)
V(g_non)$betweenness <- round(igraph::betweenness(g_non), digits = 2)
V(g_non)$centrality <- round(igraph::harmonic_centrality(g_non), digits = 2)
V(g_non)$eigen <- round(igraph::eigen_centrality(g_non)$vector, digits = 2)
V(g_non)$value <- log10(igraph::degree(g_non))

V(g_non)$color <- ifelse(V(g_non)$cohort == "Behavior Change", "#0964B0" 
                         , ifelse(V(g_non)$cohort == "Criminal Justice", "#E17F48"
                          , ifelse(V(g_non)$cohort == "JoinBodi", "#5B507A"
                            , ifelse(V(g_non)$cohort == "Media and Journalism", "#B5984F"
                             , "grey"))))

V(g_non)$shape <- ifelse(V(g_non)$grantee == "Non Grantee", "triangle", "dot")

color_map <- c(`Behavior Change` = "#0964B0"
               , `Criminal Justice` = "#E17F48"
               , `JoinBodi` = "#5B507A"
               , `Media and Journalism` = "#B5984F"
               , `Non Grantee` = "grey")

wrapped_colors <- str_wrap(names(color_map), width = 14)

igraph <- toVisNetworkData((g_non))

igraph$nodes$color <- igraph$nodes$color.background <- igraph$nodes$color

igraph$nodes$shape <- V(g_non)$shape

legend_data <- unique(igraph$nodes[, c("shape", "color")])

visNetwork(nodes = igraph$nodes 
           , edges = igraph$edges
           , main = "Endline Network") |>
  visEdges(arrows = "to") |> 
  visOptions(highlightNearest = list(enabled = TRUE, degree = 2, hover = T)
             , selectedBy = "group"
             , nodesIdSelection = TRUE) |> 
  visLegend(useGroups = FALSE
    , addNodes= data.frame(
        label = wrapped_colors
      , shape = rev(legend_data$shape)
      , color = unname(color_map)
  )) |> 
  visLayout(randomSeed = 415)

```

Each of the four cohorts' nodes is highlighted in the panels below.

::: panel-tabset
## Behavior Change

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%"}
ggraph(g_non, layout = "stress") +
  geom_edge_bundle_force(edge_color = "lightgrey", edge_linewidth = .4, alpha = .8
                  , arrow = arrow(angle = 15, length = unit(.05, "inches")
                                  , ends = "last", type = "closed")
                  , threshold = .4, n_cycle = 2) +
  geom_node_point(aes(size = degree, shape = grantee), color = "white")+
  geom_node_point(aes(size = degree, shape = grantee, color = ifelse(group == "Behavior Change", "Behavior Change", "Other")))+
  geom_node_text(aes(label = ifelse(group == "Behavior Change", acronym, NA)), size = 5, repel = TRUE, check_overlap = FALSE, max.overlaps = 20) +
  ggforce::geom_mark_hull(
    aes(x, y, group = cohort
        , label = cohort
        , filter = cohort == "Behavior Change")
    , fill = palette[[1]]
    , label.colour = palette[[1]]
    , label.fill = NA
    , label.fontsize = 16
    , con.colour = palette[[1]],
    , concavity = 4,
    expand = unit(2, "mm"),
    alpha = 0.25
  ) +
  scale_color_manual(values = c("Behavior Change" = palette[[1]], "Other" = "grey")) +
  scale_size(range = c(2, 6)) +
  #labs(title = "<span style = 'color:#0964B0;'>Behavior Change Cohort</span>")+
  theme_graph() +
  theme(legend.position = "none"
        , plot.title.position = "plot"
        , plot.title = element_markdown())
```

## Media and Journalism

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%"}
#Media and Journalism subgraph on g
ggraph(g_non, layout = "stress") +
  geom_edge_bundle_force(edge_color = "lightgrey", edge_linewidth = .4, alpha = .8
                  , arrow = arrow(angle = 15, length = unit(.05, "inches")
                                  , ends = "last", type = "closed")
                  , threshold = .4
                  , n_cycle = 2) +
  geom_node_point(aes(size = degree, shape = grantee), color = "white")+
  geom_node_point(aes(size = degree, shape = grantee, color = ifelse(group == "Media and Journalism", "Media and Journalism", "Other")))+
  geom_node_text(aes(label = ifelse(group == "Media and Journalism", acronym, NA)), size = 5, repel = TRUE, check_overlap = FALSE, max.overlaps = 20) +
  ggforce::geom_mark_hull(
    aes(x, y, group = cohort
        , label = cohort
        , filter = cohort == "Media and Journalism")
    , fill = palette[[4]]
    , label.colour = palette[[4]]
    , label.fill = NA
    , label.fontsize = 16
    , con.colour = palette[[4]],
    , concavity = 4,
    expand = unit(2, "mm"),
    alpha = 0.25
  ) +
  scale_color_manual(values = c("Media and Journalism" = palette[[4]], "Other" = "grey")) +
  scale_size(range = c(2, 6)) +
  #labs(title = "<span style = 'color:#B5984F;'>Media and Journalism Cohort</span>")+
  theme_graph() +
  theme(legend.position = "none"
        , plot.title.position = "plot"
        , plot.title = element_markdown())
```

## Criminal Justice

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%"}
#Criminal Justice subgraph on g
ggraph(g_non, layout = "stress") +
  geom_edge_bundle_force(edge_color = "lightgrey", edge_linewidth = .4, alpha = .8
                  , arrow = arrow(angle = 15, length = unit(.05, "inches")
                                  , ends = "last", type = "closed")
                  , threshold = .4
                  , n_cycle =2) +
  geom_node_point(aes(size = degree, shape = grantee), color = "white")+
  geom_node_point(aes(size = degree, shape = grantee, color = ifelse(group == "Criminal Justice", "Criminal Justice", "Other")))+
  geom_node_text(aes(label = ifelse(group == "Criminal Justice", acronym, NA)), size = 5, repel = TRUE, check_overlap = FALSE, max.overlaps = 20) +
  ggforce::geom_mark_hull(
    aes(x, y, group = cohort
        , label = cohort
        , filter = cohort == "Criminal Justice")
    , fill = palette[[2]]
    , label.colour = palette[[2]]
    , label.fill = NA
    , label.fontsize = 16
    , con.colour = palette[[2]],
    , concavity = 4,
    expand = unit(2, "mm"),
    alpha = 0.25
  ) +
  scale_color_manual(values = c("Criminal Justice" = palette[[2]], "Other" = "lightgrey")) +
  scale_size(range = c(2, 6)) +
  #labs(title = "<span style = 'color:#E17F48;'>Criminal Justice Cohort</span>")+
  theme_graph() +
  theme(legend.position = "none"
        , plot.title.position = "plot"
        , plot.title = element_markdown())

```

## JoinBodi

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%"}
#JoinBodi subgraph on g
ggraph(g_non, layout = "stress") +
  geom_edge_bundle_force(edge_color = "lightgrey", edge_linewidth = .4, alpha = .8
                  , arrow = arrow(angle = 15, length = unit(.05, "inches")
                                  , ends = "last", type = "closed")
                  , threshold = .4
                  , n_cycle = 2) +
  geom_node_point(aes(size = degree, shape = grantee), color = "white")+
  geom_node_point(aes(size = degree, shape = grantee, color = ifelse(group == "JoinBodi", "JoinBodi", "Other")))+
  geom_node_text(aes(label = ifelse(group == "JoinBodi", acronym, NA)), size = 5, repel = TRUE, check_overlap = FALSE, max.overlaps = 20) +
  ggforce::geom_mark_hull(
    aes(x, y, group = cohort
        , label = cohort
        , filter = cohort == "JoinBodi")
    , fill = palette[[3]]
    , label.colour = palette[[3]]
    , label.fill = NA
    , label.fontsize = 16
    , con.colour = palette[[3]],
    , concavity = 4,
    expand = unit(2, "mm"),
    alpha = 0.25
  ) +
  scale_color_manual(values = c("JoinBodi" = palette[[3]], "Other" = "grey")) +
  scale_size(range = c(2, 6)) +
 #labs(title = "<span style = 'color:#5B507A;'>JoinBodi Cohort</span>")+
  theme_graph() +
  theme(legend.position = "none"
        , plot.title.position = "plot"
        , plot.title = element_markdown())
```
:::

::: panel-tabset
## Cross Cohort Connectors

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%"}

# cross community nodes
communities <- V(g_non)$cohort


V(g_non)$community <- V(g_non)$cohort 

V(g_non)$names_pretty <- stringr::str_wrap(V(g_non)$name, width = 20)
#V(g_non)$filtered <- V(g_non)$grantee != "Non Grantee"

#E(g_non)$cross_community <- V(g_non)[ends(g_non, E(g_non))[,1]]$community != V(g_non)[ends(g_non, E(g_non))[,2]]$community

# Define the community to **exclude**
excluded_community <- "Non Grantee"

# Identify edges that **connect to the excluded community**
E(g_non)$involves_excluded <- V(g_non)[ends(g_non, E(g_non))[,1]]$community == excluded_community |
  V(g_non)[ends(g_non, E(g_non))[,2]]$community == excluded_community

# Identify cross-community edges **that do not involve the excluded community**
E(g_non)$cross_community <- V(g_non)[ends(g_non, E(g_non))[,1]]$community != 
  V(g_non)[ends(g_non, E(g_non))[,2]]$community & 
  !E(g_non)$involves_excluded

#Identify nodes that are at the ends of cross-community edges
cross_community_nodes <- unique(as.vector(ends(g_non, E(g_non)[E(g_non)$cross_community])))

#add an acronym column that only applies to cross-community nodes
V(g_non)$acronym_cross <- ifelse(V(g_non)$name %in% cross_community_nodes, V(g_non)$acronym, NA)


subtitle <- "<span style = 'font-size:18pt; color:#0964B0;'>**Behavior Change Cohort**</span>, <span style = 'font-size:18pt; color:#B5984F;'>**Media and Journalism Cohort**</span>, <span style = 'font-size:18pt; color:#E17F48;'>**Criminal Justice Cohort**</span>, <br><span style = 'font-size:18pt; color:#5B507A;'>**JoinBodi Cohort**</span>"

cross_cohort <- ggraph(g_non, "stress") +
  geom_edge_bundle_force(aes(alpha = !involves_excluded), edge_color = "white"
                  , edge_linewidth = .4
                         , arrow = arrow(angle = 15, length = unit(.05, "inches")
                                         , ends = "last", type = "closed"), threshold = .4, n_cycle = 2) +
  geom_node_point(aes(size = degree, shape = grantee), color = "white") +
  geom_node_point(aes(size = degree, shape = grantee, color = cohort)) +
  
  #foreground
  geom_edge_bundle_force(aes(alpha = cross_community, colour = cross_community), width = 1)+
                     #, edge_linewidth = ifelse(color = TRUE, 2, .5))
                        #, edge_linewidth = .4
                      #, alpha = .8
                      #  , arrow = arrow(angle = 15, length = unit(.05, "inches")
                      #                  , ends = "last", type = "closed"), threshold = .4, n_cycle = 2) +
   geom_node_point(aes(size = degree, shape = grantee, color = cohort)) +
   #geom_node_point(data = ggraph(g_non_delete, "stress"), aes(size = degree, shape = grantee, color = cohort)) +
   geom_node_text(aes(label = acronym_cross), size = 4, repel = TRUE
                  , max.overlaps = Inf, na.rm = TRUE
                  , nudge_y = .05
                  ) +
  #scale_edge_color_manual(values = c("TRUE" = "red", "FALSE" = "grey")) +
  scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0)) +
  scale_edge_color_manual(values = c("TRUE" = "red", "FALSE" = "white"))+
   scale_size(range = c(2, 6)) +
   scale_color_manual(values = palette)+
  # scale_edge_color_manual(values = c("grey", "red")) +
   labs(title = "Cross Cohort Connections "
        , subtitle = subtitle)+
   theme_graph() +
   theme(legend.position = "bottom"
         , plot.subtitle = ggtext::element_markdown()) +
   guides(color = "none", fill = "none")
 
cross_cohort
```

## Cross Cohort Connectors: Zoomed-in

```{r, fig.align="center", fig.width=12, fig.height=10, out.width="100%"}

cross_cohort +
  coord_cartesian(xlim = c(-6, 3), ylim = c(-8, 1))

```
:::

## Annex 2: More on Centrality Statistics

### Centrality Statistics

Global centrality statistics help understand each node's place in the overall network and whether or not they are connected to many or few other nodes in the network. Knowing this information helps to determine if an organization may be more or less influential than other organizations in the network.

Four commonly used centrality statistics are Betweenness Centrality, Closeness, Eigenvector Centrality, and Degree Centrality (overall, out, and in).

**Betweenness centrality** measures the extent to which an organization is connected to other network actors that are not connected to each other. Nodes with high betweenness serve as bridges between different parts of a network.

**Closeness** calculates the average distance between a node and all other nodes in a network. It is used to identify nodes that reach other nodes quickly. In disconnected networks, it may be necessary to use **Harmonic Centrality** instead.

**Eigenvector Centrality** is a measure of the influence of a node in a network. Those nodes that are connected to other well-connected nodes will have high eigenvector centrality scores.

**Degree Centrality** is a count of the number of connections of each node. In directed networks it can have both an **in-degree** and an **out-degree** score. The out-degree score denotes the number of connections the node initiates, and the in-degree score denotes the number of connections the node receives. The overall degree score is the sum of the in-degree and the out-degree scores.

Additionally, a network's **density** is a useful statistic to understand, but it is hard to put in context. The calculation is the number of connections divided by the total possible number of connections. A network density of 1 means that all nodes are connected to each other. This is common in small, friend group networks, but less common in real-world networks. It would not make sense for a network to be perfectly dense, and optimal density is hard to define. The endline network has a density of `{r} igraph::edge_density(g_non)`.

```{r}

dat_all1 <- dat_all |> 
  mutate(Density = paste0(round(Density, digits = 0), "%")
         , 'Avg. Harmonic Centrality \n(Closeness)' = round(`Avg. Harmonic Centrality \n(Closeness)`, digits = 2)
         , 'Avg. Betweenness' = round(`Avg. Betweenness`, digits = 2)
         , 'Avg. Eigenvector' = round(`Avg. Eigenvector`, digits = 2))

flex_fun(data = dat_all1, title = "Network Centrality Stats Compared with Simulation")

```

## Interactive Centrality Statistics

This interactive table allows readers to filter the organizations by name or sort based on the column and values.

```{r}
DT::datatable(centrality_non_end,
              caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: left;',
    'Table 1: ', htmltools::em('Centrality statistics for organizations included in the Endline network analysis sample.')
  ))

```

## Annex 2: The Organizations Included in the Endline Network

## Annex 3: R packages used in this analysis

This list contains a list of R packages used in this analysis. It does not list all of their dependencies.

:::::: columns
::: {.column width="33%"}
-   cowplot
-   extrafont
-   extrafontdb
-   flextable
-   ggalluvial
-   ggiraph
-   ggnetwork
-   ggraph
-   ggtext
-   graphlayouts
:::

::: {.column-width="33%"}
-   leaflet
-   lubridate
-   igraph
-   janitor
-   here
-   knitr
-   mapboxapi
-   networkD3
-   patchwork
-   RColorBrewer
:::

::: {.column-width="33%"}
-   readxl
-   rgeoboundaries
-   scales
-   sf
-   sfnetworks
-   sna
-   threejs
-   tidygraph
-   tidyverse
-   tmap
-   tmaptools
-   visNetwork
:::
::::::
