---
title: "Annex 5: Descriptive statistics"
format:
  html:
    toc: true
    css: prep/styles.css
execute: 
  warning: false
  message: false
  error: false
  echo: false
editor: visual
---

This document contains tables of descriptive statistics from the survey data.

```{r}
source(here::here("./prep/prep.r"))
source(here::here("./scripts/00 cleaning script.R"))
source(here::here("./scripts/01 analysis script.R"))
source(here::here("./scripts/01 descriptives.R"))


```

# Organizations

## Organization types in dataset

### Types of Organizations

```{r}

flex_fun(data = df_orgs)

```

### Grantee Organizations

```{r}
flex_fun(data = df_grantee)
```

### Voice or Teeth Organizations

```{r}

flex_fun(data = df_teeth)
```

### Organizations by Cohort

```{r}
flex_fun(data = df_orgs_cohort)

```

### Organizations by Type and Cohort

```{R}
flex_fun(data = df_orgs_desc_cohort)
```

## State-level descriptive statistics

### Organizations, by State

```{r}

flex_fun(data = df_state)

```

### Types of Organization, by State

```{r}
flex_fun(data = df_orgs_state)
```

### Cohorts, by State

```{r}
flex_fun(data = df_cohort_states)
```

# Connections

### Level of Collaboration

```{r}
flex_fun(data = df_collab_ft)
```

### Grantee and Non Grantee Collaboration

```{r}
flex_fun(data = df_collab_grantee)
```

### Level of Collaboration by Cohort

```{r}

flex_fun(data = df_collab_cohort)

```

### Frequency of Collaboration

```{r}
flex_fun(data = df_collab_freq)

```

### Level of Collaboration by Frequency

```{r}

flex_fun(data = collab_freq_level)
```

### Grantee type by Frequency of Collaboration

```{r}
flex_fun(data = df_collab_freq_grantee)
```

### Voice or Teeth Connection by Frequency

```{r}
flex_fun(data = df_collab_freq_teeth)

```

### Type of Organization Connections by Frequency

```{r}
flex_fun(data = df_collab_freq_desc_org)
```

```{r}



```
